\phantomsection
\section*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

{\em
I would like to express my deepest appreciation to all those who made this stimulating and challenging internship possible.

Firstly, I owe a debt of gratitute to my industrial mentors, Vadim Okun and Aurelien Delaitre, who chose me for this internship and supported me during those three months at NIST. I am grateful that they believed in my ability to be a fast-learner and to bring a consistent contribution to SAMATE team. Their guidance helped me to grow as a future engineer, and gave me the tools to move foward, apprehend and appreciate the research industry.

My sincere thanks also goes to Terry Cohen for her insightful advices. I loved our talks, we have always something to learn from you. You were also a wonderful reviewer for this master thesis, thank you for your precious time.

I want to express my deepest gratitude to Paul Black for welcoming my companion and I in the United States. Paul is a fabulous teacher who is always willing to share his experience and knowledge.

My thoughts goes as well to my Brazilian guy, Charles DeOliveira. Working in the same office was an amazing experience. I have no eye-deer what to say but thank you for your endless smile and your entertaining jokes.

I would like to thank the human resources for their support and for making my life easier at NIST. Thank you Barbara, Megan, and Rose, you are doing an amazing job.

I want to thank all the SAMATE team for their warm welcome. You made me feel at home, thank you for considering my thoughts, and nourishing my curiosity by answering my numerous questions.

My sincere thanks to my school, TELECOM Nancy, and my academic mentor, Muriel Duval.

And last, but not least, my special thanks goes to NIST and all its contributors, for welcoming me and giving me the opportunity to work on this challenging project.
}

\cleardoublepage